Create histogram with risk scores

### 2024-03-11 Code/03_Descriptives_save.Rmd
Final edits

png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/KM.Rec.composite.png"), width=16, height=16, units="cm", res=300)
survminer::ggsurvplot(survival::survfit(S.Rec.5.pooled ~ Center, 
                                        data=pooled.data), 
                      legend.title="",
                      legend.labs=c("Rotterdam", "Berlin", "Warsaw", "Amsterdam", "Australia"),
                      title="Recurrence-free survival",
                      ylab="Recurrence-free survival probability",
                      xlab="Time in years",
                      conf.int=TRUE, risk.table=TRUE)+
  ggplot2::guides(colour=guide_legend(nrow=2))
grDevices::dev.off()

@@

png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/KM.MSM.png"), width=16, height=16, units="cm", res=300)
survminer::ggsurvplot(survival::survfit(S.MSM.5.pooled ~ Center, 
                                        data=pooled.data), 
                      legend.title="",
                      legend.labs=c("Rotterdam", "Berlin", "Warsaw", "Amsterdam", "Australia"),
                      title="Melanoma-specific survival",
                      ylab="Melanoma-specific survival probability",
                      xlab="Time in years",
                      conf.int=TRUE, risk.table=TRUE)+
  ggplot2::guides(colour=guide_legend(nrow=2))
grDevices::dev.off()
```

>>>>

png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/KM.Rec.composite.png"), width=16, height=16, units="cm", res=300)
survminer::ggsurvplot(survival::survfit(S.Rec.5.pooled ~ Center, 
                                        data=pooled.data), 
                      legend.title="",
                      legend.labs=c("Rotterdam", "Berlin", "Warsaw", "Amsterdam", "Australia"),
                      title="Recurrence-free survival",
                      ylab="Recurrence-free survival probability",
                      xlab="Time in years",
                      conf.int=TRUE, risk.table=TRUE)+
  ggplot2::guides(colour=guide_legend(nrow=2))
grDevices::dev.off()
png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/KM.Rec.composite.zoomed.png"), width=16, height=16, units="cm", res=300)
survminer::ggsurvplot(survival::survfit(S.Rec.5.pooled ~ Center, 
                                        data=pooled.data), 
                      legend.title="",
                      legend.labs=c("Rotterdam", "Berlin", "Warsaw", "Amsterdam", "Australia"),
                      title="Recurrence-free survival",
                      ylab="Recurrence-free survival probability",
                      xlab="Time in years",
                      ylim=c(0.6, 1),
                      conf.int=TRUE, risk.table=TRUE)+
  ggplot2::guides(colour=guide_legend(nrow=2))
grDevices::dev.off()

@@

png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/KM.MSM.png"), width=16, height=16, units="cm", res=300)
survminer::ggsurvplot(survival::survfit(S.MSM.5.pooled ~ Center, 
                                        data=pooled.data), 
                      legend.title="",
                      legend.labs=c("Rotterdam", "Berlin", "Warsaw", "Amsterdam", "Australia"),
                      title="Melanoma-specific survival",
                      ylab="Melanoma-specific survival probability",
                      xlab="Time in years",
                      conf.int=TRUE, risk.table=TRUE)+
  ggplot2::guides(colour=guide_legend(nrow=2))
grDevices::dev.off()
png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/KM.MSM.zoomed.png"), width=16, height=16, units="cm", res=300)
survminer::ggsurvplot(survival::survfit(S.MSM.5.pooled ~ Center, 
                                        data=pooled.data), 
                      legend.title="",
                      legend.labs=c("Rotterdam", "Berlin", "Warsaw", "Amsterdam", "Australia"),
                      title="Melanoma-specific survival",
                      ylab="Melanoma-specific survival probability",
                      xlab="Time in years",
                      ylim=c(0.6, 1),
                      conf.int=TRUE, risk.table=TRUE)+
  ggplot2::guides(colour=guide_legend(nrow=2))
grDevices::dev.off()
```

### 2024-03-11 Code/05_FitModels_save.Rmd
Final edits

save(list=c("dd.training", "training.data.to.be.imputed", "m", 
            "imputed.training.data", "last.imputed.training.data.set", 
            "horizon", 
            "S.Rec.training", "S.MSM.training",
            "S.Rec.5.training", "S.MSM.5.training",
            "f.mi.full.Rec.5", "f.mi.BS.Rec.5", "f.mi.full.MSM.5.refit", 
            "f.mi.BS.MSM.5.refit", "MSM.cal.fact", "c.Breslow", 
            "form.full.Rec.5", "form.BS.Rec.5", "form.full.MSM.5.refit", "form.BS.MSM.5.refit"),
     file="Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata", compress=TRUE)
load("Z:/Project Melanoom/PaperMelanoma/Data/validation/validation.data.RData")
save(list=c("dd.validation", "validation.data.to.be.imputed", "m", 
            "imputed.validation.data", "last.imputed.validation.data.set", "horizon", 
            "S.Rec.validation", "S.MSM.validation", 
            "S.Rec.5.validation", "S.MSM.5.validation", "f.mi.BS.Rec.5"),
     file=paste0("Z:/Project Melanoom/PaperMelanoma/Data/validation/validation.data.Rdata"), compress=TRUE)
```

@@

>>>>

load("Z:/Project Melanoom/PaperMelanoma/Data/validation/validation.data.RData")
save(list=c("dd.validation", "validation.data.to.be.imputed", "m", 
            "imputed.validation.data", "last.imputed.validation.data.set", "horizon", 
            "S.Rec.validation", "S.MSM.validation", 
            "S.Rec.5.validation", "S.MSM.5.validation", "f.mi.BS.Rec.5"),
     file=paste0("Z:/Project Melanoom/PaperMelanoma/Data/validation/validation.data.Rdata"), compress=TRUE)
```

@@

# Calculate baseline hazards
```{r, eval=TRUE}
# baseline hazard of recurrence averaged over all imputed data sets
h0.Rec.all <- c()
for (i in 1:m){
  f.Rec.basehaz.i <- survival::basehaz(cph(form.BS.Rec.5, data=mice::complete(imputed.training.data, i), se.fit=TRUE, x=TRUE, y=TRUE))
  h0.Rec.i <- f.Rec.basehaz.i$hazard[f.Rec.basehaz.i$time==max(f.Rec.basehaz.i$time[f.Rec.basehaz.i$time<=horizon])]
  h0.Rec.all <- c(h0.Rec.all, h0.Rec.i)
}
h0.Rec <- mean(h0.Rec.all)

# baseline hazard of MSM
h0.MSM.all <- c()
for (i in 1:m){
  lp.i<-predict(f.mi.BS.Rec.5,
                newdata=mice::complete(imputed.training.data,i), 
                type="lp")
  f.MSM.basehaz.i <- survival::basehaz(rms::cph(S.MSM.5.training~lp.i,y=TRUE,x=TRUE))
  h0.MSM.i <- f.MSM.basehaz.i$hazard[f.MSM.basehaz.i$time==max(f.MSM.basehaz.i$time[f.MSM.basehaz.i$time<=horizon])]
  h0.MSM.all <- c(h0.MSM.all, h0.MSM.i)
}
h0.MSM <- mean(h0.MSM.all)
```
# Save for webapp
```{r,eval=TRUE}
save(f.mi.BS.Rec.5, MSM.cal.fact, h0.Rec, h0.MSM, c.Breslow,
     file="Z:/Project Melanoom/PaperMelanoma/Results/model.Rdata", 
     compress=TRUE)
save(list=c("dd.training", "training.data.to.be.imputed", "m", 
            "imputed.training.data", "last.imputed.training.data.set", 
            "horizon", "S.Rec.training", "S.MSM.training",
            "S.Rec.5.training", "S.MSM.5.training",
            "f.mi.full.Rec.5", "f.mi.BS.Rec.5", "f.mi.full.MSM.5.refit", 
            "f.mi.BS.MSM.5.refit", "MSM.cal.fact", "c.Breslow", "h0.Rec", "h0.MSM",
            "form.full.Rec.5", "form.BS.Rec.5", "form.full.MSM.5.refit", "form.BS.MSM.5.refit"),
     file="Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata", compress=TRUE)
```

### 2024-03-11 Code/06_CreateTablesandPlots_save.Rmd
Final edits

  colnames(BS.table) <- c("HR", "CI", "Imp.")
  assign(paste0("final.BS.table.", model), as.data.frame(BS.table))
}
```

@@

# Add C-index to model for Recurrence and MSM refit Table
```{r, eval=TRUE}
for (model in list("Rec.5", "MSM.5.refit")){
  if (model == "Rec.5"){
    # plot predict
    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/plot.predict.Rec.png"),
        width=1800, height=1800, units="px", res=300)
    plot.predict <- plot(Predict(f.mi.full.Rec.5))
    show(plot.predict)
    grDevices::dev.off()

@@

  # discrimination full and backward selected model
  for (type in c("full", "BS")){
    # load model
    f.mi <- eval(parse(text=paste0("f.mi.", type, ".", model)))
    form.mi <- eval(parse(text=paste0("form.", type, ".", model)))

@@

    final.full.table <- eval(parse(text=paste0("final.", type, ".table.", model)))
    final.full.table["Harrell's C-index", "HR"] <- sprintf("%.2f", out$cindex)
    final.full.table["Harrell's C-index", "CI"] <- paste0("[", sprintf("%.2f", out$cindex.lower),
                                                   "; ", sprintf("%.2f", out$cindex.upper), "]")
    final.full.table["Harrell's optimism-corrected C-index", "HR"] <- sprintf("%.2f", out$cindex-optimism)
    final.full.table["Harrell's optimism-corrected C-index", "CI"] <- paste0("[", sprintf("%.2f", out$cindex.lower-optimism),
                                                   "; ", sprintf("%.2f", out$cindex.upper-optimism), "]")
    final.full.table["Uno's C-index", "HR"] <- sprintf("%.2f", out$unoC)
    final.full.table["Uno's C-index", "CI"] <- paste0("[", sprintf("%.2f", out$unoC.lower),
                                                   "; ", sprintf("%.2f", out$unoC.upper), "]")
    final.full.table["AUC", "HR"] <- sprintf("%.2f", out$AUC)
    final.full.table["AUC", "CI"] <- paste0("[", sprintf("%.2f", out$AUC.lower),
                                                   "; ", sprintf("%.2f", out$AUC.upper), "]")

@@

    if (type=="BS"&model=="Rec.5"){
      CIndex.BS.Rec.5.All <- c(sprintf("%.2f", out$cindex-optimism), 
                              paste0("[", sprintf("%.2f", out$cindex.lower-optimism), 
                                     "; ", sprintf("%.2f", out$cindex.upper-optimism), "]"))
    }
  }
}
```

# Add the C-index for calibrated MSM model to Table for recurrence
```{r, eval=TRUE}
for (type in c("full", "BS")){
  f.mi <- eval(parse(text=paste0("f.mi.", type, ".Rec.5")))
  cindex.MSM <- rep(0, m)
  cindex.se.MSM <- rep(0, m)
  unoC.MSM <- rep(0, m)
  AUC.MSM <- rep(0, m)
  for (i in 1:m){
    lp.i <- predict(f.mi, newdata=mice::complete(imputed.training.data,i), type="lp")

    # Harrell's C-index
    rc <- Hmisc::rcorr.cens(-lp.i, 
                            S.MSM.5.training)
    cindex.MSM[i] <- rc["C Index"]
    cindex.se.MSM[i] <- rc["S.D."]/2

    # Uno's C-index
    Uno.data <- cbind(S.MSM.5.training[, 1], S.MSM.5.training[, 2], lp.i)
    unoC.MSM[i] <- survC1::Est.Cval(mydata=Uno.data, 
                                    tau=horizon, nofit=TRUE)$Dhat
    if (i == 1){
      unoC.boot <- c()
      nr.iter <- 40
      for (itr in 1:nr.iter){
        boot <- Uno.data[sample(1:nrow(Uno.data), nrow(Uno.data), replace=TRUE),]
        unoC <- survC1::Est.Cval(mydata=boot,
                                  tau=horizon,
                                  nofit=TRUE)$Dhat
        unoC.boot <- c(unoC.boot, unoC)
      }
      unoC.MSM.se <- PredictionTools::Rubin.combine(mean(unoC.boot), sd(unoC.boot))$se
    }

    # time-dependent ROC
    AUC.MSM.i <- timeROC::timeROC(T=S.MSM.training[, 1],
                                   delta=S.MSM.training[, 2],
                                   marker=lp.i,
                                   times=horizon,
                                   cause=1, 
                                   iid=FALSE)

    # time-dependent ROC SE
    if (i == 1){
      AUC.MSM.i <- timeROC::timeROC(T=S.MSM.training[, 1],
                                   delta=S.MSM.training[, 2],
                                   marker=lp.i,
                                   times=horizon,
                                   cause=1, 
                                   iid=TRUE)
      AUC.MSM.CI <- stats::confint(AUC.MSM.i)
      AUC.MSM.se <- as.numeric((as.numeric(AUC.MSM.CI$CI_AUC[2])/100-as.numeric(AUC.MSM.i$AUC[2]))/AUC.MSM.CI$C.alpha)
    }
    AUC.MSM[i] <- as.numeric(AUC.MSM.i$AUC[2])
  }
  cindex.mi.MSM <- Rubin.combine(cindex.MSM, cindex.se.MSM)

  final.full.table <- eval(parse(text=paste0("final.", type, ".table.Rec.5")))
  final.full.table["Harrell's C-index MSM", "HR"] <- sprintf("%.2f", cindex.mi.MSM$est)
  final.full.table["Harrell's C-index MSM", "CI"] <- paste0("[", 
    sprintf("%.2f", cindex.mi.MSM$est+qnorm(.025)*cindex.mi.MSM$se),
    "; ", sprintf("%.2f", cindex.mi.MSM$est+qnorm(.975)*cindex.mi.MSM$se), "]")
  final.full.table["Harrell's optimism-corrected C-index MSM", "HR"] <- sprintf("%.2f", cindex.mi.MSM$est-optimism)
  final.full.table["Harrell's optimism-corrected C-index MSM", "CI"] <- paste0("[", 
    sprintf("%.2f", cindex.mi.MSM$est+qnorm(.025)*cindex.mi.MSM$se-optimism),
    "; ", sprintf("%.2f", cindex.mi.MSM$est+qnorm(.975)*cindex.mi.MSM$se-optimism), "]")
  final.full.table["Uno's C-index MSM", "HR"] <- sprintf("%.2f", mean(unoC.MSM))
  final.full.table["Uno's C-index MSM", "CI"] <- paste0("[", 
    sprintf("%.2f", mean(unoC.MSM)+qnorm(.025)*unoC.MSM.se),
    "; ", sprintf("%.2f", mean(unoC.MSM)+qnorm(.975)*unoC.MSM.se), "]")
  final.full.table["AUC MSM", "HR"] <- sprintf("%.2f", mean(AUC.MSM))
  final.full.table["AUC MSM", "CI"] <- paste0("[", 
    sprintf("%.2f", mean(AUC.MSM)+qnorm(.025)*AUC.MSM.se),
    "; ", sprintf("%.2f", mean(AUC.MSM)+qnorm(.975)*AUC.MSM.se), "]")

@@

# C-index of final model for recurrence stratified by SN status
```{r, eval=TRUE}
for (arm in c("Positive", "Negative")){
  f.mi.stratified <- eval(parse(text=paste0("f.mi.BS.Rec.5")))
  S.5.subset <- S.Rec.5.training[last.imputed.training.data.set$SNstatus==arm,]

@@

# optimism-corrected
CIndex.Rec.Table <- rbind(CIndex.BS.Rec.5.All, CIndex.BS.Rec.5.Positive, CIndex.BS.Rec.5.Negative)
CIndex.Rec.Table
# utils::write.table(CIndex.Rec.Table,
#               file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/CIndex.train.txt"),
#               row.names=FALSE, col.names=FALSE, sep=",")

save(list=c("dd.training", "training.data.to.be.imputed", "m", 
            "imputed.training.data", "last.imputed.training.data.set", 
            "horizon", 
            "S.Rec.training", "S.MSM.training",
            "S.Rec.5.training", "S.MSM.5.training",
            "f.mi.full.Rec.5", "f.mi.BS.Rec.5", "f.mi.full.MSM.5.refit", 
            "f.mi.BS.MSM.5.refit", "MSM.cal.fact", "c.Breslow", "optimism",
            "form.full.Rec.5", "form.BS.Rec.5", 
            "form.full.MSM.5.refit", "form.BS.MSM.5.refit"),
     file="Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata", compress=TRUE)
```

>>>>

  # add p-values
  p.out <- anova(f.mi.BS)[, "P"]
  p.main <- c(p.out[c("SNstatus  (Factor+Higher Order Factors)")], # SN status
                  NA,               # negative SN
                  NA,               # positive SN
                  p.out[c("Age.SN",     # Age
                              "Ulceration", # Ulceration
                              "Loc_CAT")],  # Location
                  NA,               # upper limb
                  NA,               # lower limb
                  NA,               # trunk
                  NA,               # head & neck
                  NA,               # Breslow title
                  p.out[c("Breslow  (Factor+Higher Order Factors)")], # Breslow negative
                  p.out["SNstatus * Breslow  (Factor+Higher Order Factors)"], # Breslow positive
                  p.out[c("Rdamcrit")])
  BS.table <- cbind(BS.table, sprintf("%.4f", p.main))

  colnames(BS.table) <- c("HR", "CI", "Imp.", "p-value")
  assign(paste0("final.BS.table.", model), as.data.frame(BS.table))
}
```

@@

# Add C-index to model for Recurrence and MSM refit Table
```{r, eval=TRUE}
for (model in list("Rec.5", "MSM.5.refit")){
  print(model)
  if (model == "Rec.5"){
    # plot predict
    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/plot.predict.Rec.png"),
        width=1800, height=1800, units="px", res=300)
    plot.predict <- plot(Predict(f.mi.full.Rec.5))
    show(plot.predict)
    grDevices::dev.off()

@@

  # discrimination full and backward selected model
  for (type in c("full", "BS")){
    print(type)
    # load model
    f.mi <- eval(parse(text=paste0("f.mi.", type, ".", model)))
    form.mi <- eval(parse(text=paste0("form.", type, ".", model)))

@@

    final.full.table <- eval(parse(text=paste0("final.", type, ".table.", model)))
    final.full.table["Harrell's C-index", "HR"] <- sprintf("%.2f", out$HarrellC)
    final.full.table["Harrell's C-index", "CI"] <- paste0("[", sprintf("%.2f", out$HarrellC.lower),
                                                   "; ", sprintf("%.2f", out$HarrellC.upper), "]")
    final.full.table["Harrell's optimism-corrected C-index", "HR"] <- sprintf("%.2f", out$HarrellC-optimism)
    final.full.table["Harrell's optimism-corrected C-index", "CI"] <- paste0("[", sprintf("%.2f", out$HarrellC.lower-optimism),
                                                   "; ", sprintf("%.2f", out$HarrellC.upper-optimism), "]")
    final.full.table["Uno's C-index", "HR"] <- sprintf("%.2f", out$UnoC)
    final.full.table["Uno's C-index", "CI"] <- paste0("[", sprintf("%.2f", out$UnoC.lower),
                                                   "; ", sprintf("%.2f", out$UnoC.upper), "]")
    final.full.table["AUC", "HR"] <- sprintf("%.2f", out$AUC)
    final.full.table["AUC", "CI"] <- paste0("[", sprintf("%.2f", out$AUC.lower),
                                                   "; ", sprintf("%.2f", out$AUC.upper), "]")

@@

    if (type=="BS"&model=="Rec.5"){
      CIndex.BS.Rec.5.All <- c(sprintf("%.2f", out$HarrellC-optimism), 
                              paste0("[", sprintf("%.2f", out$HarrellC.lower-optimism), 
                                     "; ", sprintf("%.2f", out$HarrellC.upper-optimism), "]"))
    }
  }
}
```

# Add the C-index for calibrated MSM model to Table for recurrence
```{r, eval=TRUE}
for (type in c("full", "BS")){
  print(type)
  f.mi <- eval(parse(text=paste0("f.mi.", type, ".Rec.5")))
  HarrellC.MSM <- rep(0, m)
  HarrellC.MSM.se <- rep(0, m)
  UnoC.MSM <- rep(0, m)
  UnoC.MSM.se <- rep(0, m)
  AUC.MSM <- rep(0, m)
  AUC.MSM.se <- rep(0, m)
  for (i in 1:m){
    # linear predictor ith prediction
    lp.i <- predict(f.mi, newdata=mice::complete(imputed.training.data,i), type="lp")
    f.MSM.lp.i <- survival::coxph(S.MSM.5.training ~ lp.i)

    # Harrell's C-index
    rc.H <- survival::concordance(f.MSM.lp.i, timewt = "n")
    HarrellC.MSM[i] <- rc.H$concordance
    HarrellC.MSM.se[i] <- sqrt(rc.H$var)

    # Uno's C-index
    rc.U <- survival::concordance(f.MSM.lp.i, timewt = "n/G2")
    UnoC.MSM[i] <- rc.U$concordance
    UnoC.MSM.se[i] <- sqrt(rc.U$var)

    # time-dependent ROC
    AUC.MSM.i <- timeROC::timeROC(T=S.MSM.training[, 1],
                                   delta=S.MSM.training[, 2],
                                   marker=lp.i,
                                   times=horizon,
                                   cause=1,
                                   iid=TRUE)
    AUC.MSM[i] <- as.numeric(AUC.MSM.i$AUC[2])
    AUC.MSM.CI <- stats::confint(AUC.MSM.i)
    AUC.MSM.se[i] <- as.numeric((as.numeric(AUC.MSM.CI$CI_AUC[2])/100-as.numeric(AUC.MSM.i$AUC[2]))/AUC.MSM.CI$C.alpha)
  }
  HarrellC.mi.MSM <- Rubin.combine(HarrellC.MSM, HarrellC.MSM.se)
  Uno.mi.MSM <- Rubin.combine(UnoC.MSM, UnoC.MSM.se)
  AUC.mi.MSM <- Rubin.combine(AUC.MSM, AUC.MSM.se)

  final.full.table <- eval(parse(text=paste0("final.", type, ".table.Rec.5")))
  final.full.table["Harrell's C-index MSM", "HR"] <- sprintf("%.2f", HarrellC.mi.MSM$est)
  final.full.table["Harrell's C-index MSM", "CI"] <- paste0("[",
    sprintf("%.2f", HarrellC.mi.MSM$est+qnorm(.025)*HarrellC.mi.MSM$se),
    "; ", sprintf("%.2f", HarrellC.mi.MSM$est+qnorm(.975)*HarrellC.mi.MSM$se), "]")
  final.full.table["Harrell's optimism-corrected C-index MSM", "HR"] <- sprintf("%.2f", HarrellC.mi.MSM$est-optimism)
  final.full.table["Harrell's optimism-corrected C-index MSM", "CI"] <- paste0("[",
    sprintf("%.2f", HarrellC.mi.MSM$est+qnorm(.025)*HarrellC.mi.MSM$se-optimism),
    "; ", sprintf("%.2f", HarrellC.mi.MSM$est+qnorm(.975)*HarrellC.mi.MSM$se-optimism), "]")
  final.full.table["Uno's C-index MSM", "HR"] <- sprintf("%.2f", Uno.mi.MSM$est)
  final.full.table["Uno's C-index MSM", "CI"] <- paste0("[",
    sprintf("%.2f", Uno.mi.MSM$est+qnorm(.025)*Uno.mi.MSM$se),
    "; ", sprintf("%.2f", Uno.mi.MSM$est+qnorm(.975)*Uno.mi.MSM$se), "]")
  final.full.table["AUC MSM", "HR"] <- sprintf("%.2f", AUC.mi.MSM$est)
  final.full.table["AUC MSM", "CI"] <- paste0("[",
    sprintf("%.2f", AUC.mi.MSM$est+qnorm(.025)*AUC.mi.MSM$se),
    "; ", sprintf("%.2f", AUC.mi.MSM$est+qnorm(.975)*AUC.mi.MSM$se), "]")

@@

# C-index of final model for recurrence stratified by SN status
```{r, eval=FALSE}
for (arm in c("Positive", "Negative")){
  f.mi.stratified <- eval(parse(text=paste0("f.mi.BS.Rec.5")))
  S.5.subset <- S.Rec.5.training[last.imputed.training.data.set$SNstatus==arm,]

@@

# optimism-corrected
CIndex.Rec.Table <- rbind(CIndex.BS.Rec.5.All, CIndex.BS.Rec.5.Positive, CIndex.BS.Rec.5.Negative)
CIndex.Rec.Table
# utils::write.table(CIndex.Rec.Table,
#               file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/CIndex.train.txt"),
#               row.names=FALSE, col.names=FALSE, sep=",")
```

```{r,eval=TRUE}
save(list=c("dd.training", "training.data.to.be.imputed", "m", 
            "imputed.training.data", "last.imputed.training.data.set", 
            "horizon", 
            "S.Rec.training", "S.MSM.training",
            "S.Rec.5.training", "S.MSM.5.training",
            "f.mi.full.Rec.5", "f.mi.BS.Rec.5", "f.mi.full.MSM.5.refit", 
            "f.mi.BS.MSM.5.refit", "MSM.cal.fact", "h0.Rec", "h0.MSM",
            "c.Breslow", "optimism",
            "form.full.Rec.5", "form.BS.Rec.5", 
            "form.full.MSM.5.refit", "form.BS.MSM.5.refit"),
     file="Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata", compress=TRUE)
```

### 2024-03-11 Code/08_CreateNomogram_save.Rmd
Final edits

# baseline hazard of recurrence averaged over all imputed data sets
h0.Rec.all <- c()
for (i in 1:m){
  f.Rec.basehaz.i <- basehaz(cph(form.BS.Rec.5, data=mice::complete(imputed.training.data, i), se.fit=TRUE, x=TRUE, y=TRUE))
  h0.Rec.i <- f.Rec.basehaz.i$hazard[f.Rec.basehaz.i$time==max(f.Rec.basehaz.i$time[f.Rec.basehaz.i$time<=horizon])]
  h0.Rec.all <- c(h0.Rec.all, h0.Rec.i)
}
h0.Rec <- mean(h0.Rec.all)

@@

save(list=c("dd.training", "training.data.to.be.imputed", "m", 
            "imputed.training.data",  "last.imputed.training.data.set", 
            "horizon", 
            "S.Rec.training", "S.MSM.training",
            "S.Rec.5.training", "S.MSM.5.training",
            "f.mi.full.Rec.5", "f.mi.BS.Rec.5", "f.mi.full.MSM.5.refit", 
            "f.mi.BS.MSM.5.refit", "MSM.cal.fact", "c.Breslow", "optimism",
            "form.full.Rec.5", "form.BS.Rec.5", 
            "form.full.MSM.5.refit", "form.BS.MSM.5.refit", 
            "rc.Rec", "int.Rec", "h0.Rec"),
     file="Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata", compress=TRUE)
```

>>>>

@@

save(list=c("dd.training", "training.data.to.be.imputed", "m", 
            "imputed.training.data",  "last.imputed.training.data.set", 
            "horizon", 
            "S.Rec.training", "S.MSM.training",
            "S.Rec.5.training", "S.MSM.5.training",
            "f.mi.full.Rec.5", "f.mi.BS.Rec.5", "f.mi.full.MSM.5.refit", 
            "f.mi.BS.MSM.5.refit", "MSM.cal.fact", "h0.Rec", "h0.MSM",
            "c.Breslow", "optimism",
            "form.full.Rec.5", "form.BS.Rec.5", 
            "form.full.MSM.5.refit", "form.BS.MSM.5.refit", 
            "rc.Rec", "int.Rec", "h0.Rec"),
     file="Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata", compress=TRUE)
```

### 2024-03-11 Code/09_CreateRiskScoreHistogram_save.Rmd
Final edits

# baseline hazard of MSM
h0.MSM.all <- c()
lp.MSM.all <- c()
for (i in 1:m){
  lp.i<-predict(f.mi.BS.Rec.5,
                newdata=mice::complete(imputed.training.data,i), 
                type="lp")
  lp.MSM.all <- cbind(lp.MSM.all, lp.i)
  f.MSM.basehaz.i <- basehaz(rms::cph(S.MSM.5.training~lp.i,y=TRUE,x=TRUE))
  h0.MSM.i <- f.MSM.basehaz.i$hazard[f.MSM.basehaz.i$time==max(f.MSM.basehaz.i$time[f.MSM.basehaz.i$time<=horizon])]
  h0.MSM.all <- c(h0.MSM.all, h0.MSM.i)
}
h0.MSM <- mean(h0.MSM.all)
lp.MSM <- rowMeans(lp.MSM.all)

# TODO: Is this correct?
lp.MSM.all[3,]

@@

save(rc.Rec, int.Rec, f.mi.BS.Rec.5, MSM.cal.fact, max.range,
     file="Z:/Project Melanoom/PaperMelanoma/Results/model.Rdata", 
     compress=TRUE)

save(list=c("dd.training", "training.data.to.be.imputed", "m", 
            "imputed.training.data", "last.imputed.training.data.set", 
            "horizon", 
            "S.Rec.training", "S.MSM.training",
            "S.Rec.5.training", "S.MSM.5.training",
            "f.mi.full.Rec.5", "f.mi.BS.Rec.5", 
            "f.mi.full.MSM.5.refit", "f.mi.BS.MSM.5.refit", 
            "MSM.cal.fact", "c.Breslow", "optimism",
            "form.full.Rec.5", "form.BS.Rec.5", 
            "form.full.MSM.5.refit", "form.BS.MSM.5.refit", 
            "rc.Rec", "int.Rec", "h0.Rec", "lp.points.Rec.5",
            "rc.MSM", "rc.Rec", "h0.MSM", "lp.points.MSM.5",
            "lp.Rec", "lp.MSM", "max.breaks", "h.Rec",
            "h.plot", "y.lim.hist", "x.lim", "coef.Rec", "center.Rec"),
     file="Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata", compress=TRUE)
```

>>>>

@@

save(list=c("dd.training", "training.data.to.be.imputed", "m", 
            "imputed.training.data", "last.imputed.training.data.set", 
            "horizon", 
            "S.Rec.training", "S.MSM.training",
            "S.Rec.5.training", "S.MSM.5.training",
            "f.mi.full.Rec.5", "f.mi.BS.Rec.5", 
            "f.mi.full.MSM.5.refit", "f.mi.BS.MSM.5.refit", 
            "MSM.cal.fact", "c.Breslow", "optimism",
            "form.full.Rec.5", "form.BS.Rec.5", 
            "form.full.MSM.5.refit", "form.BS.MSM.5.refit", 
            "rc.Rec", "int.Rec", "h0.Rec", "lp.points.Rec.5",
            "rc.MSM", "rc.Rec", "h0.MSM", "lp.points.MSM.5",
            "max.breaks", "h.Rec",
            "h.plot", "y.lim.hist", "x.lim", "coef.Rec", "center.Rec"),
     file="Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata", compress=TRUE)
```
